The \prob

### 2013-03-20 byzantine/byzantine.tex
byz: small fixes

We show that the Spoken Words plan, with some number $m$, is an answer to the \prob for more than three times $m$ many heads, as long as there are $m$ or fewer bad guys.

@@

As we saw from the situations in Figures 1 and 2, it is the fact that bad guys can lie that makes the \prob so hard.
The problem becomes easier to find an answer for if we can make sure they don't lie. One way to do this is to let the heads send signed letters to each other. Using computers, there are ways to sign your letters where you use some very big numbers that make it very hard for a bad guy to pretend a signed letter was written by someone else or says something different. We'll suppose the heads use this way of signing letters. So, already supposing A1, A2, and A3, we will also suppose the following: \\
\\
\begin{tabular}{p{0.8em}p{0.8em}p{0.9\textwidth}}
A4 & (a) &
A bad guy can't write a signed letter and pretend that a good guy wrote it, and also can't change a signed
letter that was already written to say something else. \\
& (b) & Anyone can make sure that a signed letter came from the person who signed it.
\end{tabular} \\

>>>>

We show that the Spoken Words plan, with some number $m$, is an answer to the \prob~for more than three times $m$ many heads, as long as there are $m$ or fewer bad guys.

@@

As we saw from the situations in Figures 1 and 2, it is the fact that bad guys can lie that makes the \prob~so hard.
The problem becomes easier to find an answer for if we can make sure they don't lie. One way to do this is to let the heads send signed letters to each other. Using computers, there are ways to sign your letters where you use some very big numbers that make it very hard for a bad guy to pretend a signed letter was written by someone else or says something different. We'll suppose the heads use this way of signing letters. So, already supposing A1, A2, and A3, we will also suppose the following: \\
\\
\begin{tabular}{p{0.8em}p{0.8em}p{0.9\textwidth}}
A4 & (a) &
A bad guy can't write a signed letter and pretend that a good guy wrote it, and also can't change a signed
letter that was already written to say something else. \\
& (b) & Anyone can make sure that a signed letter came from the person who signed it.
\end{tabular} \\
